\begin{comment}

According to Luria, purposeful movement is the output of multilevel planning process. It presumes certain goal to be accomplished. 

- The first stage is the general planning, this level answers the question why and how some action should be performed. 

- On the second level, concrete motion patterns are generated on the basis of general plan. These motion patterns are referred as motion melodies. Motion melodies are the sequences of the motions, ordered in time, which should allow accomplishment of the goal. 

- On the third level ”orders” are generated to the direction of the spinal cord. On this level, melody of the motions is implemented. 

The present work is targeted towards detecting disorders on the second and third levels.  Digital Luria’s alternating series test are selected for this purpose.

- The first Luria’s alternating series test: tracing the series requires one to follow the periodic pattern. Tested individual asked to follow periodic pattern, for example sinusoidal line see ”Fig 5” or the line consisting of the strait segments ”Fig 4” (here and after referred as PL - line), with the pen. 

- The second Luria’s alternating test: coping the series requires one to copy periodic pattern. Pattern is drawn on top of the paper and tested individual is asked to draw the same on the bottom of the paper see ”Fig 2 and 3”. 

- The third test: continuing the series, requires one to continue periodic pattern (PL line). Few segments of the pattern are drawn on the paper and tested individual is asked to continue the pattern see ”Fig 1”. 

In a non digitalized case, the neurologist or psychiatrist does assessment visually. If all the tests are problematic for the tested individual then the disorder is most likely on the third level where motion melody is outputted to the spine. Some of the Luria’s tests are quite simple and do not require to generate complicated motion melodies. If the problem appears only during the third (more complicated test), and either do not appear at all or less severe for a simpler tests, then most likely disorder is on the second level where motion melodies are generated.

\end{comment}

